Online Verification of Commutativity

### 2020-10-04 acmPaper/paper.tex
tweak in figure 1

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \centering
        \begin{verbatim}
        var a : meters = 1;
        var b : miles = (miles) a;
        var c : feet = (feet) a;
        define wugs:
            1 mile = 10000 wugs;
            1 foot = 10 wugs;
        var d : wugs = (wugs) a;
        \end{verbatim}
        \vspace{-3ex}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}

>>>>

\begin{figure}[]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \centering
        \begin{verbatim}
        var x : meters = 1;
        define foot:
            1 meter = 3.28 feet;
        define miles:
            1 meter = 0.000621 miles;
        define wugs:
            1 mile = 10000 wugs;
            1 foot = 10 wugs;
        var y : wugs = (wugs) x;
        \end{verbatim}
        \vspace{-3ex}
        \caption{A sample program with user defined type conversion.}
    \end{subfigure}
